hbm_paper_results

### 2024-03-19 paper_prop_results.Rmd

@@

visualize magnitude of sex-biases

@@

cent.feat.sex.test.df %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  ggplot() +
  geom_dotplot(aes(x=prop, y=median_sex_diff, color=dataset, fill=dataset), binaxis = "y", stackdir="center") +
    facet_grid(pheno_cat~dataset, scales="free_y", labeller=labeller(dataset=dataset_names)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

#zoom in on combat-GAM vs combat-LS
cent.feat.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  #mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              #TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= dataset, color=dataset), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~prop, labeller = as_labeller(percent_f), scales="free") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

cent.feat.sex.test.df %>%
  group_by(dataset, prop) %>%
  summarize(min_diff = min(median_sex_diff)*100, max_diff=max(median_sex_diff)*100)
```

Look at differences in M:F for subjects w very high or very low centiles
```{r}
feat_exts_long <- ratio.df %>%
  dplyr::select(-contains(c("diff", ".z"))) %>%
  pivot_longer(cols=c(pheno_list), names_to="pheno", values_to="centile_cat") %>%
   mutate(pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_))) %>%
  mutate(centile_cat = case_when(. < 0.2 ~ "low",
                                        . > 0.8 ~ "high", 
                                        TRUE ~ "mid"))
feat_exts_long %>%
  dplyr::filter(centile_cat == "low") %>%
  ggplot() +
  geom_bar(aes(x=pheno_cat, fill=sex, color=sex)) +
  facet_grid(prop ~ dataset)

feat_exts_long %>%
  dplyr::filter(centile_cat == "high") %>%
  ggplot() +
  geom_bar(aes(x=pheno_cat, fill=sex, color=sex)) +
  facet_grid(prop ~ dataset)
```

@@

```{r}
#trying to add stats test
global_sex_diffs <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno %in% vol_list_global & dataset %in% c("cf.gam", "cf.gamlss")) %>%
  mutate(pheno_prop = paste(pheno, prop, sep="&"))

@@

```{r}
sex_err_ratio.plt <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff = diff*100,
         pheno_prop = paste(pheno, prop, sep="&")) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  # scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  # scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Centile Error", x = "% Females in Imbalanced Site") +
  stat_pvalue_manual(stat_merge2, label = "p.val_fdr.signif", label.size = 3, tip.length = 0, hide.ns = TRUE, remove.bracket = TRUE) +
  scale_x_discrete(labels=percent_f) +
  # facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2, strip.position = "right") +
  # guides(x = ggh4x::guide_axis_nested(delim = "&", inv=TRUE)) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  labs(fill="Sex", color="Sex")+
  facet_grid(dataset ~ pheno, labeller=labeller(dataset=dataset_names), scales="free_x")
  # ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
sex_err_ratio.plt
```

look at just cf.gam & cf.gamlss

```{r, eval=FALSE}
cent.feat.sex.test.df %>%
  dplyr::filter(dataset == "cf.gamlss") %>%
  dplyr::select(pheno, prop, sig_fdr) %>%
  arrange(pheno, prop)
```

Plot on brains for 60% F imbalance:
```{r, eval=FALSE}
aseg_cerebrum <- readRDS(file="/Users/megardn/Desktop/BGD_Repos/ggseg_atlas/aseg_cerebrum_atlas.RDS")

cent.feat.sex.test.df2 <- cent.feat.sex.test.df %>%
  dplyr::filter(prop == "prop-04") %>%
  mutate(pheno_cat = as.factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)),
    label = sub("_[^_]*_", "_", pheno)) #for plotting
sex_t_tests_to_plot <- left_join(cent.feat.sex.test.df2, dk.parc, by="label")

# max(sex_t_tests_to_plot$median_sex_diff)*100
# min(sex_t_tests_to_plot$median_sex_diff)*100

dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
#var plot
sex.var.plot.df <- sex_t_tests_to_plot %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         # median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
         #                      TRUE ~ median_sex_diff*100)) %>%
         median_sex_diff = median_sex_diff*100) %>%
  group_by(dataset, pheno_cat)

tp <- unique(sex.var.plot.df[,c('dataset','pheno_cat')]) %>%
  dplyr::filter(dataset=="ukb_CN")
tp$sex_diff <- 1

sex.var.plot <- ggplot(sex.var.plot.df) +
  geom_rect(data = tp, fill="gray", xmin = -Inf, xmax = Inf,
            ymin = -Inf, ymax = Inf, alpha = 0.4) +
  ggseg::geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = median_sex_diff)) +
  #scale_fill_gradient2() +
  facet_grid(dataset ~ pheno_cat, labeller = labeller(dataset = as_labeller(dataset_names))) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", limits = c(-3, 3), name = "Sex Effect") #
#sex.var.plot

#plot global
sex.var.plot.global.df <- sex_t_tests_to_plot %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  dplyr::filter(!grepl('_refA', dataset)) %>% #drop refA levels
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE)) %>%
  dplyr::select(!c(label, region, hemi)) %>% #drop cols corresponding to dk regions
  mutate(tissue_class = as.factor(case_when(pheno == "GMV" ~ "cGM",
                                            pheno == "Ventricles" ~ "CSF",
                                            pheno == "WMV" ~ "WM",
                                            pheno == "sGMV" ~ "sGM",
                                            TRUE ~ NA)),
        # median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
        #                       TRUE ~ median_sex_diff*100)) %>% #drop NS values
        median_sex_diff = median_sex_diff*100) %>%
  group_by(dataset)

tp <- unique(sex.var.plot.global.df[,c('dataset','pheno_cat')]) %>%
  dplyr::filter(dataset=="ukb_CN")
tp$sex_standard <- 1

sex.var.plot.global <- ggplot(sex.var.plot.global.df) +
  geom_rect(data = tp, fill="gray", xmin = -Inf,xmax = Inf,
            ymin = -Inf, ymax = Inf, alpha = 0.4) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             aes(fill = median_sex_diff),
             side = c("coronal")) +
  #scale_fill_gradient2() +
  facet_grid(dataset~pheno_cat) + 
  theme_linedraw(base_size=12) +
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", limits = c(-3, 3),  name = "Sex Effect") #,
# sex.var.plot.global

#Combine plots - need to keep playing around to make the spacing pretty when it saves out

p_sex <- ggarrange(
  sex.var.plot.global, sex.var.plot,
  ncol=2, nrow=1, 
  widths = c(1, 3.1),
  #labels=c("A", "B"),
  #hjust=0.01,
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

p_sexannotate <- annotate_figure(p_sex, top = text_grob("Figure 2A. Sex-biases in centile score errors across combat configurations when Imbalanced Site has 70% Female", 
               color = "black", size = 14, hjust=.65))
p_sexannotate
```

@@

comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=comp, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap( ~ full_df)
```
Test sex-biases in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.feat.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list)
```

@@

@@

```{r}
z.subj.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.subj.sex.test.df <- bind_rows(z.subj.sex.test.list)
```

```{r}
z.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

Test sex-biases in z errors w/in each feature

```{r}
noext_z.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext_z.subj.sex.test.df <- bind_rows(noext_z.subj.sex.test.list)
```

@@

```{r}
noext_z.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

>>>>

simple bar-plot to count regions w sigificant sex-differences in errors

@@

visualize magnitude of sex-biases (directional magnitude of errors within pheno cat)

@@

#just global volumes
cent.feat.sex.test.df %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  ggplot() +
  geom_dotplot(aes(x=prop, y=median_sex_diff, color=dataset, fill=dataset), binaxis = "y", stackdir="center") +
    facet_grid(pheno_cat~dataset, scales="free_y", labeller=labeller(dataset=dataset_names)) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  scale_fill_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

#zoom in on combat-GAM vs combat-LS
cent.feat.sex.test.df %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  #mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              #TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= dataset, color=dataset), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_wrap(~prop, labeller = as_labeller(percent_f), scales="free") +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

```{r, eval=FALSE}
#stats test
global_sex_diffs <- cent.feat.sex.test.df %>%
  dplyr::filter(pheno %in% vol_list_global & dataset %in% c("cf.gam", "cf.gamlss")) %>%
  mutate(pheno_prop = paste(pheno, prop, sep="&"))

@@

```{r, eval=FALSE}
sex_err_ratio.plt <- ratio.df %>%
  dplyr::select(participant, sex, age_days, sim.site, prop, dataset, paste0("diff_", vol_list_global)) %>%
  dplyr::filter(dataset == "cf.gam" | dataset == "cf.gamlss") %>%
  pivot_longer(cols=starts_with("diff_"), names_to="pheno", names_prefix="diff_", values_to = "diff") %>%
  mutate(dataset = factor(dataset, levels = c("ukb_CN", "cf", "cf.lm", "cf.gam", "cf.gamlss"), ordered = TRUE),
         pheno = factor(pheno, levels = c("GMV", "sGMV", "Ventricles", "WMV"), ordered = TRUE),
         diff = diff*100,
         pheno_prop = paste(pheno, prop, sep="&")) %>% #for visuals
  ggplot() +
  geom_violin(aes(x=prop, y=diff, fill=sex, color=sex)) +
  theme_linedraw(base_size = 11) +
  # scale_fill_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  # scale_color_manual(values=c(cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF"), name = "ComBat \nConfiguration", labels=dataset_names) +
  labs(y="Centile Error", x = "% Females in Imbalanced Site") +
  stat_pvalue_manual(stat_merge2, label = "p.val_fdr.signif", label.size = 3, tip.length = 0, hide.ns = TRUE, remove.bracket = TRUE) +
  scale_x_discrete(labels=percent_f) +
  # facet_wrap(~dataset, labeller=labeller(dataset=dataset_names), nrow=2, strip.position = "right") +
  # guides(x = ggh4x::guide_axis_nested(delim = "&", inv=TRUE)) +
  theme(plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "bottom") +
  labs(fill="Sex", color="Sex")+
  facet_grid(dataset ~ pheno, labeller=labeller(dataset=dataset_names), scales="free_x")
  # ggtitle("Errors in centile scores of global features in ComBat-GAM and ComBatLS")
sex_err_ratio.plt
```

@@

comp.df %>%
  dplyr::filter(sig_fdr==TRUE) %>%
ggplot() +
  geom_bar(aes(x=comp, fill=bigger_group)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap( ~ full_df)
```

Test sex-differences in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.feat.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list)
```

simple bar-plot to count regions w significant sex-differences

@@

visualize magnitude of sex-biases (directional magnitude of errors within pheno cat)

```{r}
noext_cent.feat.sex.test.df <- noext_cent.feat.sex.test.df %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)))

noext_cent.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff*100)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

noext_t.test.cent.sex.diff <- noext_cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(
           # p.val_fdr < 0.001 ~ "***",
           #                     p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
           #                     p.val_fdr >= 0.01 & 
                               p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = ifelse(max_val < 0, ((max_val*100)*0.5), (max_val*100)+0.8))

noext_cent.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff*100) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = noext_t.test.cent.sex.diff[which(noext_t.test.cent.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Centile Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)

#compare with full dataset
cortical_cent_sex_diff.plt
```
similar overall pattern

@@

Test w/in feature sex-differences in errors (diff_list) using `featurewise_sex_bias_test.R`, saved as `full_featurewise_cent_sex_bias_tests.RDS`

```{r}
z.sex.test.list <- readRDS(paste0(data_path, "/full_featurewise_z_sex_bias_tests.RDS"))
z.feat.sex.test.df <- bind_rows(z.sex.test.list)
```

simple bar-plot to count regions w significant sex-differences

```{r}
z.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

visualize magnitude of sex-biases (directional magnitude of errors within pheno cat)

```{r}
z.feat.sex.test.df <- z.feat.sex.test.df %>%
  mutate(pheno=gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)))

z.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

t.test.z.sex.diff <- z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(
           # p.val_fdr < 0.001 ~ "***",
           #                     p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
           #                     p.val_fdr >= 0.01 & 
                               p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = ifelse(max_val < 0, ((max_val)*0.5), (max_val)+0.05))

z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = t.test.z.sex.diff[which(t.test.z.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
```

@@

Test sex-diffs in z errors w/in each feature

```{r}
noext_z.feat.sex.test.list <- readRDS(paste0(data_path, "/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext_z.feat.sex.test.df <- bind_rows(noext_z.feat.sex.test.list)
```

@@

```{r}
noext_z.feat.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

visualize magnitude of sex-biases (directional magnitude of errors within pheno cat)

```{r}
noext_z.feat.sex.test.df <- noext_z.feat.sex.test.df %>%
  mutate(pheno=gsub(".z", "", pheno)) %>%
  mutate(pheno_cat = factor(case_when(
    pheno %in% vol_list_global ~ "Global Volume",
    pheno %in% vol_list_regions ~ "Regional Volume",
    pheno %in% sa_list ~ "Regional SA",
    pheno %in% ct_list ~ "Regional CT",
    TRUE ~ NA_character_)))

noext_z.feat.sex.test.df %>%
  mutate(median_sex_diff = case_when(sig_fdr == FALSE ~ NA,
                              TRUE ~ median_sex_diff)) %>%
  ggplot() +
  geom_histogram(aes(x=median_sex_diff, fill= pheno_cat, color=pheno_cat), alpha=0.4, position = "identity") +
  geom_vline(xintercept = 0, linetype="dashed") +
  facet_grid(prop~dataset, scales="free")

noext_t.test.z.sex.diff <- noext_z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  group_by(dataset, pheno_cat, prop) %>%
  summarise(t.test.p = tidy(t.test(median_sex_diff, mu=0))$p.value,
            max_val = max(median_sex_diff)) %>% #test median of each distribution against 0
  mutate(p.val_fdr = p.adjust(t.test.p, method="fdr", n = (3*4*11)), #not testing global vols, too few data points
                  sig_fdr_tf = case_when(p.val_fdr < 0.05 ~ TRUE,
                                      p.val_fdr >= 0.05 ~ FALSE),
         sig_fdr = case_when(
           # p.val_fdr < 0.001 ~ "***",
           #                     p.val_fdr >= 0.001 & p.val_fdr < 0.01 ~ "**",
           #                     p.val_fdr >= 0.01 & 
                               p.val_fdr < 0.05 ~ "*",
                               p.val_fdr >= 0.05 ~ ""),
         y_pos = ifelse(max_val < 0, ((max_val)*0.5), (max_val)+0.05))

noext_z.feat.sex.test.df %>%
  dplyr::filter(pheno_cat != "Global Volume" & dataset != "cf") %>%
  mutate(median_sex_diff = median_sex_diff) %>%
  ggplot(aes(x=prop, y=median_sex_diff)) +
  geom_boxplot(aes(color=dataset)) +
    facet_grid(dataset~pheno_cat, labeller=labeller(dataset=dataset_names)) + 
  geom_text(aes(label = sig_fdr, y = y_pos),
              data = noext_t.test.z.sex.diff[which(noext_t.test.z.sex.diff$dataset != "cf"),]) +
  theme_linedraw() +
  scale_color_manual(values=c(cf= "#440D54", cf.gam = "#3D75C2", cf.lm = "#75C23D", cf.gamlss ="#CFB023FF")) +
  theme(legend.position="none", plot.title = element_text(size=12), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  labs(y="Median Male - Female Z Error", x = "% Females in Imbalanced Site") +
  scale_x_discrete(labels=percent_f)
```
